Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-03-27 chi/piecework/presentation/presentation.tex
fleshed out sections and frames

\usepackage{tikz,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor}
\usepackage[citestyle=author,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

@@

% PAPER ROADMAP
% Open problems in crowdsourcing: complexity, decomposition, relationships
% Piecework!
% Wait what's piecework again
% Some cool case studies: 
%     airy's computers
%     domestic/farmhand labor
%     matchstick girls
%     industrial workers
% Okay let's get into this
% Complexity limits
%     what did crowdsourcing say?
%     what did piecework say?
%     comparisons?
%     implications?
% Decomposition limits
%     what did crowdsourcing say?
%     what did piecework say?
%     comparisons?
%     implications?
% Worker relationships
%     what did crowdsourcing say?
%     what did piecework say?
%     comparisons?
%     implications?
% Discussion
%     this is a very tricky thing to do, predicting the future
%     anyway let's predict the future: utopian/dystopian visions
%     Research agendas! go go gadget contextual analysis

@@

\begin{frame}{Open problems in crowdsourcing}
\begin{itemize}[<+- | alert@+>]
  \item Complexity~\cite{suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364}
  \item Decomposition
  \item Relationships
\end{itemize}
\end{frame}

\begin{frame}{Emerging field of on--demand work}
\begin{itemize}[<+- | alert@+>]
  \item what's that about??
\end{itemize}
\end{frame}

@@

    % \faTwitter
    name: {Ali Alkhatib} \\
    email: \href{mailto:ali.alkhatib@cs.stanford.edu}{ali.alkhatib@cs.stanford.edu} \\
    twitter: \href{https://twitter.com/_alialkhatib}{@\_alialkhatib} \\
\end{frame}

>>>>

\usepackage{tikz,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

\definecolor{PineGreen}{HTML}{008800}
\definecolor{Red}{HTML}{FF0000}
\definecolor{Blue}{HTML}{0000FF}
\definecolor{JokeGreen}{HTML}{00C953}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}
\newcommand{\ali}[1]{{\color{Red}[al2: #1]}}

@@

% ## Intro [`1 minute`] [`1`]
% - Open problems in crowdsourcing: complexity, decomposition, relationships [`?`]
% - Piecework! [`?`]
% ## Wait what's piecework again [`1 minute`] [`2`]
% ## Some case studies: [`3 minutes`] [`5`]
% - airy's computers [`1`]
% - domestic/farmhand labor [`0.5`]
% - matchstick girls [`1`]
% - industrial workers [`0.5`]
% ## Complexity limits [`3 minutes`] [`8`]
% - what did crowdsourcing say? [`0.5`]
% - what did piecework say? [`1`]
% - comparisons? [`1`]
% - implications? [`0.5`]
% ## Decomposition limits [`3 minutes`] [`11`]
% - what did crowdsourcing say? [`0.5`]
% - what did piecework say? [`1`]
% - comparisons? [`1`]
% - implications? [`0.5`]
% ## Worker relationships [`3 minutes`] [`14`]
% - what did crowdsourcing say? [`0.5`]
% - what did piecework say? [`1`]
% - comparisons? [`1`]
% - implications? [`0.5`]
% ## Discussion [`1 minute`] [`15`]
% - this is a very tricky thing to do, predicting the future [`?`]
% - anyway let's predict the future: utopian/dystopian visions [`?`]
% - Research agendas! go go gadget contextual analysis [`?`]

@@

\begin{frame}{Open problems in crowdsourcing
                                                                                [\texttt{1 minute}]
}
\begin{itemize}[<+- | alert@+>]
  \item Complexity~\cite{suzukiAtelier,KimStoria,yuanAlmost,
                         YuEncouragingOutside,
                         Nebeling:2016:WCW:2858036.2858169,
                         Hahn:2016:KAB:2858036.2858364}
  \item Decomposition
  \item Relationships
\end{itemize}
\end{frame}

\section{Piecework Primer}
\begin{frame}{Piecework Review
                                                                                [\texttt{1 minute}]
}
something
\end{frame}

\section{Case Studies}
\begin{frame}{Airy's Computers
                                                                                [\texttt{1 minute}]
    }
\begin{itemize}
  \item images of hand--drawn tables
  \item maybe some illustration of the mathematical work that was being done
  \item draw to attention that you could break this into pieces
        (an example of breaking a formula down?)
\end{itemize}
\end{frame}

\begin{frame}{Domestic \& Farmhand Labor
                                                                                [\texttt{0.5 minutes}]
}
\end{frame}

\begin{frame}{The Match Girls
                                                                                [\texttt{1 minute}]
}
\end{frame}

\begin{frame}{Industrial Workers
                                                                                [\texttt{0.5 minutes}]
}
\end{frame}

\section{Research Threads}
\begin{frame}{Complexity Limits
                                                                                [\texttt{3 minutes}]
}
\begin{itemize}[<+- | alert@+>]
  \item Crowdwork's perspective
  \item Piecework's perspective
  \item Comparisons
  \item Implications
\end{itemize}
\end{frame}

\begin{frame}{Decomposition Limits
                                                                                [\texttt{3 minutes}]
}
\begin{itemize}[<+- | alert@+>]
  \item Crowdwork's perspective
  \item Piecework's perspective
  \item Comparisons
  \item Implications
\end{itemize}
\end{frame}

\begin{frame}{Worker Relationships
                                                                                [\texttt{3 minutes}]
}
\begin{itemize}[<+- | alert@+>]
  \item Crowdwork's perspective
  \item Piecework's perspective
  \item Comparisons
  \item Implications
\end{itemize}
\end{frame}

\section{Discussion}
\begin{frame}{Discussion
                                                                                [\texttt{1 minute}]
}
\end{frame}

@@

    name: {Ali Alkhatib} \\
    email: \href{mailto:ali.alkhatib@cs.stanford.edu}{ali.alkhatib@cs.stanford.edu} \\
    twitter: \href{https://twitter.com/_alialkhatib}{@\_alialkhatib} \\
\end{frame}
